Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-22 paper/paper.tex
Distinguishing between core results and other
ACM keywords
ACM Whitelist of packages

@@

In the dynamic scenario, we assume that the physical substrate network is a~tree of height one.
That is, every physical machine (leaf) is connected directly to the root (that has no hosting capabilities).
A single physical machine hosts a fixed number of virtual machines.
The model restricted to such networks becomes a variant of online graph clustering.
That is, we are given a~set of~$n$ nodes (virtual machines) with time-varying pairwise
communication patterns, which have to be partitioned into~$\ell$~physical machines, each of
capacity $k=n/\ell$.

@@

\item \emph{Where to migrate, and what?}
If an algorithm decides to collocate nodes $x$ and~$y$, the~question becomes
how. Should $x$ be migrated to the physical machine holding $y$, $y$ to the one holding
$x$, or should both nodes be migrated to a new machine?

@@

\section{Lower bound $\Omega(k\cdot \ell)$}

\maciek{I assume $\alpha = 1$ to simplify calculations, but everything should hold for general $\alpha$}

@@

@@

    \section{An $O(kl)$-competitive Algorithm For the Scenario With the Perfect Partition}

@@

          \section{$O(k)$-competitive algorithm for the ring}

@@

\todo{Check ACM package whitelist (especially these algorithm environments)}

>>>>

\keywords{online algorithms, competitive analysis, etc}

@@

We assume that the physical substrate network is a~tree of height one.
That is, every physical machine (leaf) is connected directly to the root (that has no hosting capabilities).
A single physical machine hosts a fixed number of virtual machines.
The model restricted to such networks becomes a variant of online graph clustering.
That is, we are given a~set of~$n$ nodes (virtual machines) with time-varying pairwise
communication patterns, which have to be partitioned into~$\ell$~physical machines, each of
capacity $k=n/\ell$.

@@

h\item \emph{Where to migrate, and what?}
If an algorithm decides to collocate nodes $x$ and~$y$, the~question becomes
how. Should $x$ be migrated to the physical machine holding $y$, $y$ to the one holding
$x$, or should both nodes be migrated to a new machine?

@@

\section{Core results}
\subsection{Lower bound $\Omega(k\cdot \ell)$}

@@

\section{Additional results (most likely should be deleted)}

@@

@@

          \subsection{$O(k)$-competitive algorithm for the ring}

@@

\todo{Include e-mails}

\todo{Check ACM package whitelist}

\todo{Replace package algorithmpseudocode, it is not whitelisted https://www.acm.org/publications/taps/whitelist-of-latex-packages}
